The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-13 paper.tex
update

  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0$ -- $1.2$ Myr,\
  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
  $8\times10^{55}$ -- $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

  %, and prevent the disk from destruction by .
  % ablate

@@

The jet

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed may\
      lead to stochastic acceleration of CRe, and balanced with radiative cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\end{itemize}

>>>>

  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
  The jet duration (1.2 Myr) allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
  $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

@@

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed\
      will leads to stochastic acceleration of CRe, and probably balanced with radiative cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\end{itemize}
